Title

### 2013-03-08 inc/gun/gun_model.tex
merge remaining comments in extension section

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the electric field that nears this aperture turns outward, causing the anode itself to act as a negative lens. %TODO reference
Additionally, the longitudinal electric field stregth sharply decreases near the anode.
Because the front of the pulse sees this change before the back, this changing field acts as a pulse compression element.

@@

To first model the longitudinal (compression) action at the anode %TODO ref
on electrons that are a distance $z$ ahead or behind of the center of the pulse feel a slightly different field, 
\begin{equation}
  F_z(0,z^{\prime} - z) \approx F_z(0,z^{\prime} - z) + \frac{\partial F_z}{\partial z^{\prime}} z
\end{equation}
As noted before, the constant leading term does not contribute to the intrapulse dynamic, however the second term is of the proper form to say that in this region
\begin{equation}
  M_z = \frac{\partial F_z}{\partial z^{\prime}}
\end{equation}

To model the radial action (negative lensing), we can expand for electrons that are a distance $r$ radially outward from the center of the pulse,
\begin{equation}
  F_r(r,z^{\prime}) \approx F_r(r,z^{\prime}) + \frac{\partial F_r}{\partial r^{\prime}} r
\end{equation}
without an analytic form for $F$, we can appeal to Gauss' law (in absense of external charge)
\begin{equation}
  \frac{\partial F_x}{\partial x^{\prime}} + \frac{\partial F_y}{\partial y^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 2 \frac{\partial F_{\smallT}}{\partial r^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 0
\end{equation}
to see that
\begin{equation}
  M_{\smallT} = -\frac{1}{2}\frac{\partial F_z}{\partial z^{\prime}}
\end{equation}

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation}
  F_z(0,z^{\prime}) = \frac{qV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form (demonstrated in Section \ref{sec:gun_design}) the lensing constants are then
\begin{gather}
  M_{\smallT} = -\frac{qVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{qVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right)
\end{gather}

>>>>

In the acceleration region of a UEM column, a constant electric field is applied to the newly created electron pulse, increasing its velocity until it achieves its ultimate velocity just upon leaving the region at the anode aperture.
As seen in Section \ref{sec:const_force}, this constant electric field does not affect the intrapulse dynamics, however the electric field that nears this aperture turns outward, causing the anode itself to act as a negative transverse lens. %TODO reference
Additionally, the longitudinal electric field stregth sharply decreases near the anode.
Because the front of the pulse sees this change before the back, this changing field acts as a pulse compression element.

@@

To first model the longitudinal (compression) action at the anode %TODO ref
on electrons that are a distance $z$ ahead or behind of the center of the pulse feel a slightly different field, 
\begin{equation}
  F_z(0,z^{\prime} - z) \approx F_z(0,z^{\prime} - z) + \frac{\partial F_z}{\partial z^{\prime}} z
\end{equation}
Again, the constant leading term does not contribute to the intrapulse dynamic, however the second term is of the proper form to say that in this region the anode's longitudinal compression strength $M_z$ is given by
\begin{equation}
  M_z = \frac{\partial F_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

To model the radial action (negative transverse lensing), we can expand the radial force $F_r$ for electrons that are a distance $r$ radially outward from the center of the pulse,
\begin{equation}
  F_r(r,z^{\prime}) \approx F_r(r,z^{\prime}) + \frac{\partial F_r}{\partial r^{\prime}} r
\end{equation}
Without an analytic form for $F$, we can appeal to Gauss' law (in absense of external charge)
\begin{gather}
  \frac{\partial F_x}{\partial x^{\prime}} + \frac{\partial F_y}{\partial y^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 2 \frac{\partial F_{\smallT}}{\partial r^{\prime}} + \frac{\partial F_z}{\partial z^{\prime}} = 0 \\
  \Rightarrow \frac{\partial F_{\smallT}}{\partial r^{\prime}} = - \frac{1}{2} \frac{\partial F_z}{\partial z^{\prime}}
\end{gather} 
to see that the transverse lens traverse lens strength $M_{\smallT}$ from the anode is simply,
\begin{equation}
  M_{\smallT} = -\frac{1}{2}\frac{\partial F_z}{\partial z^{\prime}} \, \text{.}
\end{equation}

We may choose to assume that the on-axis field is defined as a smoothed step down function
\begin{equation} \label{eq:anode_tanh}
  F_z(0,z^{\prime}) = \frac{qV}{2z^{\prime}_A} \left( 1 - \tanh \left( \frac{ z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \right)
\end{equation}
where $V$ is the accelerating potential, $z^{\prime}_A$ is the position of the anode (the cathode assumed to be at $z^{\prime} = 0$) and $s$ is a constant quantifying the ``sharpness'' of the fall-off of the electric field.
Indeed, this form is analgous to the super-Gaussian envalope (\ref{eq:reg_of_influence}), however it is open ended on the cathode side, which is necessary for the electrons to be accelerated away from the photocathode.
Given this form (demonstrated in Section \ref{sec:gun_design}) the ``lensing'' strengths are then
\begin{gather}
  M_{\smallT} = -\frac{qVs}{4z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \\
  M_z = \frac{qVs}{2z^{\prime 2}_A} \operatorname{sech}^2 \left( \frac{z^{\prime} - z^{\prime}_A }{ z^{\prime}_A / s } \right) \, \text{.}
\end{gather}
As with the RF cavity, remember to include the on-axis force (\ref{eq:anode_tanh}) in the overall pulse propagation.
